An example exploratory analysis script

### 2024-08-05 code/analysis-code/analysisfile.qmd

```{r}
aggresid <- group_fit %>% filter(is_aggregated(Crime.Category)) %>% select(td) %>% gg_tsresiduals()

@@

```{r}
murdresid <- group_fit %>% filter(Crime.Category == 'MURDER') %>% select(td) %>% gg_tsresiduals()

@@

```{r}
agglb <- augment(filter(group_fit, is_aggregated(Crime.Category))) %>% 
  features(.resid, ljung_box, l = 24) %>% gt()

@@

```{r}
murdlb <- augment(filter(group_fit, Crime.Category == 'MURDER')) %>% 
  features(.resid, ljung_box, l = 24) %>% gt()

>>>>

```{r}
theme_set(theme_gray())
aggresid <- group_fit %>% filter(is_aggregated(Crime.Category)) %>% select(td) %>% gg_tsresiduals()

@@

```{r}
theme_set(theme_gray())
murdresid <- group_fit %>% filter(Crime.Category == 'MURDER') %>% select(td) %>% gg_tsresiduals()

@@

```{r}
theme_set(theme_minimal())
agglb <- augment(filter(group_fit, is_aggregated(Crime.Category))) %>% 
  features(.resid, ljung_box, l = 24) %>% gt()

@@

```{r}
theme_set(theme_minimal())
murdlb <- augment(filter(group_fit, Crime.Category == 'MURDER')) %>% 
  features(.resid, ljung_box, l = 24) %>% gt()

### 2024-08-05 code/eda-code/eda.qmd

```{r}
dayline <- d1 %>% group_by(Occurred.Date) %>% 
  summarize(
  cnt = n()
) %>% as.data.frame() %>% 
  ggplot(mapping = aes(x=Occurred.Date, y=cnt)) +
  geom_line() +
  labs(title = 'Austin Crime Over Time', x = 'Time of Occurence (by day)', y = 'Count')

@@

```{r}
monthline <- d1 %>% filter(Occurred.Date <= '2024-03-31') %>%
  mutate(Occurred.Date = trunc.Date(Occurred.Date, 'months')) %>% 
  group_by(Occurred.Date) %>% 
  summarize(
  cnt = n()
) %>% as.data.frame() %>% 
  ggplot(mapping = aes(x=Occurred.Date, y=cnt)) +
  geom_line() +
  labs(title = 'Austin Crime Over Time', x = 'Time of Occurence (by month)', y = 'Count')

@@

```{r}
murdline <- d1 %>% filter(Occurred.Date <= '2024-03-31', Crime.Category == 'MURDER') %>%
  mutate(Occurred.Date = trunc.Date(Occurred.Date, 'months')) %>% 
  group_by(Occurred.Date) %>% 
  summarize(
  cnt = n()
) %>% as.data.frame() %>% 
  ggplot(mapping = aes(x=Occurred.Date, y=cnt)) +
  geom_line() +
  labs(title = 'Austin Murder Over Time', x = 'Time of Occurence (by month)', y = 'Count')

>>>>

```{r}
dayline <- d1 %>% group_by(Occurred.Date) %>% 
  summarize(
  cnt = n()
) %>% as.data.frame() %>% 
  ggplot(mapping = aes(x=Occurred.Date, y=cnt)) +
  geom_line() +
  labs(title = 'Austin Crime Over Time', x = 'Time of Occurence (by day)', y = 'Count') +
  theme(panel.background = element_rect(fill = 'white',
                                        color = 'white'),
        plot.background = element_rect(fill = 'white',
                                        color = 'white')
        )

@@

```{r}
monthline <- d1 %>% filter(Occurred.Date <= '2024-03-31') %>%
  mutate(Occurred.Date = trunc.Date(Occurred.Date, 'months')) %>% 
  group_by(Occurred.Date) %>% 
  summarize(
  cnt = n()
) %>% as.data.frame() %>% 
  ggplot(mapping = aes(x=Occurred.Date, y=cnt)) +
  geom_line() +
  labs(title = 'Austin Crime Over Time', x = 'Time of Occurence (by month)', y = 'Count') +
  theme(panel.background = element_rect(fill = 'white',
                                        color = 'white'),
        plot.background = element_rect(fill = 'white',
                                        color = 'white')
        )

@@

```{r}
murdline <- d1 %>% filter(Occurred.Date <= '2024-03-31', Crime.Category == 'MURDER') %>%
  mutate(Occurred.Date = trunc.Date(Occurred.Date, 'months')) %>% 
  group_by(Occurred.Date) %>% 
  summarize(
  cnt = n()
) %>% as.data.frame() %>% 
  ggplot(mapping = aes(x=Occurred.Date, y=cnt)) +
  geom_line() +
  labs(title = 'Austin Murder Over Time', x = 'Time of Occurence (by month)', y = 'Count') +
  theme(panel.background = element_rect(fill = 'white',
                                        color = 'white'),
        plot.background = element_rect(fill = 'white',
                                        color = 'white')
        )
